---
title: "Scripts"
output: 
  html_document:
    template: ../assets/template.html
    css: ../assets/style.css
editor_options: 
  markdown: 
    wrap: sentence
---

# Data Processing Scripts

There are four types of R-scripts in this repository, each with a separate folder.

-   [`custom_functions/`](https://github.com/stefanvermeent/abcd_ddm/tree/main/scripts/custom_functions): Custom R-functions written for this project
-   [`0_simulations/`](https://github.com/stefanvermeent/abcd_ddm/tree/main/scripts/0_simulations): Simulation scripts for power and DDM analyses
-   [`1_data_prep/`](https://github.com/stefanvermeent/abcd_ddm/tree/main/scripts/1_data_prep): Data processing scripts
-   [`2_analyses/`](https://github.com/stefanvermeent/abcd_ddm/tree/main/scripts/2_analyses): Primary and exploratory analysis scripts

Each script takes an input(s) and produces output(s).
All outputs are stored in [analysis_objects/](https://github.com/stefanvermeent/abcd_ddm/tree/main/analysis_objects).
The tables below provides an overview of the inputs and outputs of each script.

```{r include = FALSE}
library(tidyverse)
```


```{r echo = FALSE}

file_list <- list.files(pattern = ".R$", full.names = T, recursive = T) %>% 
  map_df(function(x){
    script_text <- 
      read_lines(x) %>% 
      str_subset("load.*(RData|csv)|save.image\\(.*\\)|file = .*RData|filename = .*pdf|write_csv.*csv") %>% 
      str_remove_all("glue|\\{.*\\}| |\"|\\(|\\)|,") %>% 
      str_c(collapse = " ") %>% 
      str_replace_all("load","input: ") %>% 
      str_replace("save|write_csv|save.imagefile = |save.image|filename = |file = ","~output: ") %>% 
      str_replace_all("save|write_csv|save.imagefile = |save.image|filename = |file = ","output: ") %>% 
      str_split("~", simplify = T)
    
    tibble(
      dir       = x %>% str_remove_all("\\./") %>% str_remove_all("/.*") %>% str_remove("^\\d-"),
      script    = x %>% str_remove_all(".*/"),
      raw       = script_text %>% str_squish() %>% str_c(collapse = ", "),
      n_input   = str_count(script_text[1], "input"),
      input1    = script_text[1],
      input2    = input1 %>% str_remove_all("input: ") %>% str_trim(),
      input     = input2 %>% str_split(" ", simplify = T) %>% str_remove_all(".*/") %>% str_c(collapse = "<br> ") %>% ifelse(. == "<br> ","",.),
      n_output  = str_count(script_text[2], "output") %>% ifelse(is.na(.), 0, .),
      output1   = script_text[2],
      output2   = output1 %>% str_remove_all("output: ") %>% str_trim(),
      output    = output2 %>% str_split(" ", simplify = T) %>% str_remove_all(".*/") %>% str_c(collapse = "<br> ") %>%  ifelse(. == "<br> NA","",.)
    )
  }) 

```


### Simulations

```{r, echo = FALSE, results='asis'}
simulations <- 
  file_list %>% 
  select(dir, script, input, output) %>% 
  filter(dir == "0_simulations") %>% 
  select(-dir) 
cat(
  "|script|input|output|",
  "|------|-----|------|",
  glue::glue_data(
    simulations,
    "|{script}|{input}|{output}|"
  ),
  sep = "\n"
)
```

### Data Prep

```{r, echo = FALSE, results='asis'}
data_prep <- 
  file_list %>% 
  select(dir, script, input, output) %>% 
  filter(dir == "1_data_prep") %>% 
  select(-dir) 
cat(
  "|script|input|output|",
  "|------|-----|------|",
  glue::glue_data(
    data_prep,
    "|{script}|{input}|{output}|"
  ),
  sep = "\n"
)
```

### Analyses

```{r, echo = FALSE, results='asis'}
analyses <- 
  file_list %>% 
  select(dir, script, input, output) %>% 
  filter(dir == "2_analyses") %>% 
  select(-dir)
cat(
  "|script|input|output|",
  "|------|-----|------|",
  glue::glue_data(
    analyses,
    "|{script}|{input}|{output}|"
  ),
  sep = "\n"
)
```